---
title: "DATA 607 Homework 3"
author: "James Williams"
output:
  html_document:
    df_print: paged
---

#1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

##Import Data
```{r}
library(RCurl) 
x <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv") 
college_majors <- read.csv(text = x)
head(college_majors)
```

##Identify Majors with "DATA" or "STATISTICS"

```{r}
library(tidyverse)
data_majors <- str_subset(college_majors$Major, "DATA")
statistics_majors <- str_subset(college_majors$Major, "STATISTICS")
data_majors
statistics_majors
```

#2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
fruits <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'

fruits <- str_split(fruit, "  ")
fruits <- gsub('[0-9]+', '', fruits)
fruits
```

#3 Describe, in words, what these expressions will match:
"(.)\1\1"  Matches words with any character two times.

"(.)(.)\\2\\1" Matches words with 2 consecutive character pairs and a character pair before and after the first character pair.

"(..)\1" Matches words with a character grouping; e.g. a character pair repeated.

"(.).\\1.\\1" Matches words with repeated character pairs spaced by 1 character in between.

"(.)(.)(.).*\\3\\2\\1" Matches words with any three character pairs repeated three times.


#4 Construct regular expressions to match words that:

Start and end with the same character: "^.*$"
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.): 
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}
str_view("racecar", "^(.)(.*)\\1$")
str_view("church", "([A-Za-z][A-Za-z]).*\\1")
str_view("eleven", "([A-Za-z]).*\\1.*\\1.")
```